Short Paper

### 2023-04-05 manuscript/manuscript.qmd
Align at 72 spaces

> Personally, I have never experienced \[eye discomfort\] because I get vaccinated and I am protected including other staff. However, we realize that the air can badly affect other people and patients who come to this place.

>>>>

> Personally, I have never experienced \[eye discomfort\] because I get
> vaccinated and I am protected including other staff. However, we
> realize that the air can badly affect other people and patients who
> come to this place.
